### 2010-03-17 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: more things todo, I'm afraid.
Desc@ICFP: clean-up \note{}s. Update todo.
Desc@ICFP: apply \toDesc on tagged description.
Desc@ICFP: uniform Fig.~\ref

\subsection{A universe of descriptions}

@@

\note{Check Martin-Lof reference}

@@

Again, this is a clear reminiscence of the ``sum-of-products'' style:
we have a finite sum of constructors. Of course, every description can
be expressed in this style, using a singleton as single constructor if
necessary.
\note{I think we need a function mapping a $\TagDesc$ to the
  corresponding $\Desc$. This function should go here.}

@@

Then, we have to translate the notion of algebra in our dependent
setting. This is achieved by the predicate $\All{D}{X}{P}{x}$
(Fig.\ref{fig:all-predicates}) that, intuitively, states that
$\Bhab{P}{X \To \Set}$ holds everywhere in $x$. Based on that
knowledge, we ought to be able to prove that $P$ holds for
$\Con{xs}$. We close our elimination principle by taking an argument
$x$ in $\Mu{D}$ and claiming that the motive $P$ is realised on $x$.

>>>>

\subsection{A universe of descriptions}
\label{sec:desc-universe}

@@

@@

Again, this is a clear reminiscence of the ``sum-of-products'' style:
we have a finite sum of constructors. Of course, every description can
be expressed in this style, using a singleton as single constructor if
necessary. A tagged description can trivially be turned into a
full-blown description. We note $\toDesc{TD}$ the description computed
from the tagged description $TD$.

@@

Then, we have to translate the notion of algebra in our dependent
setting. This is achieved by the predicate $\All{D}{X}{P}{x}$
(Fig.~\ref{fig:all-predicates}) that, intuitively, states that
$\Bhab{P}{X \To \Set}$ holds everywhere in $x$. Based on that
knowledge, we ought to be able to prove that $P$ holds for
$\Con{xs}$. We close our elimination principle by taking an argument
$x$ in $\Mu{D}$ and claiming that the motive $P$ is realised on $x$.

### 2010-03-17 papers/icfp-2010-desc/paper_type_theory.tex
Desc@ICFP: clean-up \note{}s. Update todo.
Desc@ICFP: uniform Fig.~\ref

The rules ensuring Context Validity (Fig.\ref{fig:context-validity})
are unsurprisingly common. They simply guarantee the validity of the
empty context, as well as the linear extension of a context by a
well-typed variable.

@@

The typing judgements (Fig.\ref{fig:typing-judgements}) are just as
familiar. We recognise the standard presentation of $\Pi$ and $\Sigma$
types, respectively inhabited by lambda terms and dependent
pairs. Naturally, there are rules for function application and
projections of $\Sigma$-types. Equal types can be substituted, thanks
to the conversion rule.

@@

Dually to type synthesis, type checking judgements
(Fig.\ref{fig:type-checking}) act as \emph{sinks}. From an expression
$\exprIn$ and a type propagated down to it, they elaborate a low-level
term. The strength of this approach comes from the availability of the
type to drive the elaboration of expressions. Its benefit on lambda
abstraction and pairs is well-known. Let us explore the consequences
on our coding scheme for finite sets.

@@

\note{ This might deserve a more thorough explanation, with snippet of
       code. }

>>>>

The rules ensuring Context Validity (Fig.~\ref{fig:context-validity})
are unsurprisingly common. They simply guarantee the validity of the
empty context, as well as the linear extension of a context by a
well-typed variable.

@@

The typing judgements (Fig.~\ref{fig:typing-judgements}) are just as
familiar. We recognise the standard presentation of $\Pi$ and $\Sigma$
types, respectively inhabited by lambda terms and dependent
pairs. Naturally, there are rules for function application and
projections of $\Sigma$-types. Equal types can be substituted, thanks
to the conversion rule.

@@

Dually to type synthesis, type checking judgements
(Fig.~\ref{fig:type-checking}) act as \emph{sinks}. From an expression
$\exprIn$ and a type propagated down to it, they elaborate a low-level
term. The strength of this approach comes from the availability of the
type to drive the elaboration of expressions. Its benefit on lambda
abstraction and pairs is well-known. Let us explore the consequences
on our coding scheme for finite sets.

@@

\note{This might deserve a more thorough explanation, with snippet of
  code.}
